Matching bullets

### 2015-11-20 imaging-paper.Rnw
start and end of lines defined

\begin{figure}
\centering
    \subfloat[Loess smooth at $x = 100$ (span is 0.03).\label{fig:smooth}]{%
<<smooth, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=3, out.width='.49\\textwidth', warning=FALSE>>=
lofX <- lofX %>% group_by(bullet) %>% mutate(
  l30 = smoothloess(y, resid, span = 0.03)
)
lofX$r05 <- 0.75* sign(lofX$l30) * as.numeric(abs(lofX$l30) > .75)
lofX$type <- factor(lofX$r05)
levels(lofX$type) <- c("groove", NA, "peak")

qplot(data=lofX, y, resid, colour=bullet, size=I(1)) +
  geom_line(aes(y=l30), colour="grey30") +
  facet_grid(bullet~.) +
  scale_colour_brewer("", palette="Set1") +
  theme_bw() +
  theme(legend.position="none")
@
    }
    \hfill
    \subfloat[Values above/below a threshold level are defined as peaks and grooves. \label{fig:smoothcutb}]{%
<<smoothcut, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=4, out.width='.49\\textwidth', warning=FALSE>>=
qplot(data=lofX, x=y, y=l30, colour=type, geom="line", group=bullet) + 
  facet_grid(bullet~.) +
  ylab("Individual characteristics") + 
  geom_point(aes(y=r05)) +
  scale_colour_brewer(palette="Set2", na.value = "grey90") +
  theme_bw() +
  theme(legend.position="bottom")
@
    }
\hfill
    \subfloat[ \label{fig:smoothcutc}]{%
<<smoothtile, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=2.5, out.width='.49\\textwidth'>>=
qplot(data=lofX, x=y, y=bullet, fill=type, geom="tile") +
  scale_fill_brewer(palette="Set2", na.value="grey90") + 
  theme_bw() +
  ylab("") +
  theme(legend.position="bottom")
@
    }    
\caption{\label{fig:smoothcut} Processing surface crosscuts.}
\end{figure}

>>>>

\begin{figure}
\centering
    \subfloat[Loess smooth at $x = 100$ (span is 0.03).\label{fig:smooth}]{%
<<smooth, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=3.5, out.width='.49\\textwidth', warning=FALSE>>=
lofX <- lofX %>% group_by(bullet) %>% mutate(
  l30 = smoothloess(y, resid, span = 0.03)
)
lofX$r05 <- 0.75* sign(lofX$l30) * as.numeric(abs(lofX$l30) > .75)
lofX$type <- factor(lofX$r05)
levels(lofX$type) <- c("groove", NA, "peak")

qplot(data=lofX, y, resid, colour=bullet, size=I(0.5), geom="line", group=bullet) +
  geom_line(aes(y=l30), colour="grey30", size=0.75) +
  facet_grid(bullet~.) +
  scale_colour_brewer("", palette="Set1") +
  theme_bw() +
  theme(legend.position="none")
@
    }
    \hfill
    \subfloat[Values above/below a threshold level are defined as peaks and grooves. \label{fig:smoothcutb}]{%
<<smoothcut, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=4, out.width='.49\\textwidth', warning=FALSE>>=
qplot(data=lofX, x=y, y=l30, colour=type, geom="line", 
      group=bullet, size = I(0.75)) + 
  facet_grid(bullet~.) +
  ylab("Individual characteristics") + 
#  geom_point(aes(y=r05)) +
  geom_rect(xmin = 200, xmax = 2260, ymin = -.75, ymax = 0.75, colour=NA, fill=alpha("grey90", alpha =0.5)) +
  scale_colour_brewer(palette="Set2", na.value = "grey90") +
  theme_bw() +
  theme(legend.position="bottom")
@
    }
\hfill
    \subfloat[Overlaps of the same color indicate matching striation marks.  \label{fig:smoothcutc}]{%
<<smoothtile, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=2.5, out.width='.49\\textwidth'>>=
qplot(data=lofX, x=y, y=bullet, fill=type, geom="tile") +
  scale_fill_brewer(palette="Set2", na.value="grey90") + 
  theme_bw() +
  ylab("") +
  theme(legend.position="bottom")
@
    }    
\caption{\label{fig:match} Matching striation marks: smooth (a), cut (b), and match (c).}
\end{figure}

\hh{Figure~\ref{fig:match} gives an overview of the automated matching routine: after smoothing the scan with a loess of a very small span, shown in (a), we define a striation mark as a groove or a peak if it exceeds a pre-set threshold (of 0.75$\mu m$; XXX need to vary over this threshold level next). Two lines are defined as a match, if their peak/groove base at the threshold overlaps. If there is no overlap, a peak/groove leads to a mismatch. We then count the number of maximum consecutive matches. }
